### 2023-03-29 main/chapter_experiment.tex
add jet resolution

\paragraph{Electrons.}
Electrons are measured by both tracking in the inner detector and calorimetry
in the electromagnetic calorimeter.
These two measurements give two complementary inputs that aid in electron
reconstruction.
As for muons, the resolution from tracking scales with $1/\pt$, but the
calorimetry error is dominated by Poisson statistics with a number of charged
particles that scales in proportion to the electron energy $E$.
Combining these two factors with a constant baseline noise, one can therefore
model the relative electron resolution as
\begin{equation}
\label{eqn:experiment_electron_resolution}
\frac{\sigma(E)}{E}
\approx
\frac{a_1}{\sqrt{E}}
\oplus
\frac{a_2}{\pt}
\oplus
a_3
\end{equation}
in which $\oplus$ indicates a sum in quadrature.
In \atlas, these $a_i$ parameters are roughly
$a_1 \approx 0.1\,\sqrt{\eV[G]}$,
$a_2 \approx 0.25\,\eV[G]$, and
$a_3 \approx 0.007$~\cite{nackenhorst2010top, Lester:705139, ERDMANN201418}.
Although resolutions vary across the solid angle, this formula roughly
reproduces the reported resolutions of
$\frac{\sigma(E)}{E} \approx 4\%$ at $E = \pt = 10\,\eV[G]$,
$\frac{\sigma(E)}{E} \approx 1\%$ at $E = \pt = 100\,\eV[G]$, and
$\frac{\sigma(E)}{E} \approx 0.1\%$ at
$E = \pt = 1\,\eV[T]$ for electrons~\cite{atlas2019electron}.

@@

\paragraph{Jets.}
\begin{equation}
\label{eqn:experiment_jet_resolution}
\frac{\sigma(E)}{E}
\approx
\frac{b_1}{\sqrt{E}}
\oplus
b_2
\end{equation}
with
$b_1 \approx 0.5\,\sqrt{\eV[G]}$ and
$b_2 \approx 0.03$.

>>>>

\paragraph{Electrons.}
Electrons are measured by both tracking in the inner detector and calorimetry
in the electromagnetic calorimeter.
These two measurements give two complementary inputs that aid in electron
reconstruction.
As for muons, the resolution from tracking scales with $1/\pt$, but the
calorimetry error is dominated by Poisson statistics with a number of charged
particles that scales in proportion to the electron's energy.
Combining these two factors with a constant baseline noise, one can therefore
model the relative electron resolution as
\begin{equation}
\label{eqn:experiment_electron_resolution}
\frac{\sigma(\pt)}{\pt}
\approx
\frac{a_1}{\sqrt{\pt}}
\oplus
\frac{a_2}{\pt}
\oplus
a_3
,
\end{equation}
in which $\oplus$ indicates a sum in quadrature.
To describe \atlas, these $a_i$ parameters are roughly
$a_1 \approx 0.1\,\sqrt{\eV[G]}$,
$a_2 \approx 0.25\,\eV[G]$, and
$a_3 \approx 0.007$~\cite{nackenhorst2010top, Lester:705139, ERDMANN201418}.
Although resolutions vary across the solid angle, this formula roughly
reproduces the reported electron resolutions of
$\frac{\sigma(\pt)}{\pt} \approx 4\%$ at $\pt = 10\,\eV[G]$,
$\frac{\sigma(\pt)}{\pt} \approx 1\%$ at $\pt = 100\,\eV[G]$, and
$\frac{\sigma(\pt)}{\pt} \approx 0.1\%$ at
$\pt = 1\,\eV[T]$~\cite{atlas2019electron}.

@@

\paragraph{Jets.}
Although charged hadrons are tracked in the inner detector, the total energy of
jets also depends vitally on neutral hadrons, which are only observed through
their hadronic interactions in the calorimeter system.
With less influence from tracking, calorimetry noise is the dominant
contribution to the experimental resolution on hadronic jets.
However, other noise contributions arising from electrical signals and pile-up
scale in proportion in $1/\pt$.
one can therefore again approximate \atlas's relative jet energy resolution as
\begin{equation}
\label{eqn:experiment_jet_resolution}
\frac{\sigma(\pt)}{\pt}
\approx
\frac{b_1}{\sqrt{\pt}}
\oplus
\frac{b_2}{\pt}
\oplus
b_3
,
\end{equation}
the same functional form as for electrons in
Equation~\ref{eqn:experiment_electron_resolution},
with
$b_1 \approx 1.0\,\sqrt{\eV[G]}$
$b_2 \approx 0.5\,\eV[G]$, and
$b_3 \approx 0.03$~\cite{atlas2021jetresolution}.
This formula approximately describes the measured jet resolutions of
$\frac{\sigma(\pt)}{\pt} \approx 20\%$ at $\pt = 30\,\eV[G]$,
$\frac{\sigma(\pt)}{\pt} \approx 8\%$ at $\pt = 200\,\eV[G]$, and
$\frac{\sigma(\pt)}{\pt} \approx 4\%$ at
$\pt = 2\,\eV[T]$~\cite{atlas2021jetresolution}.

Note that hadronic weak decays can produce real, not-prompt missing momentum
in jets.
This effect can skew jet reconstruction distributions towards low energies,
and is particularly prominent for heavy-flavour jets~\cite{nackenhorst2010top}.
